---
title: 
##date: "August 1, 2024"
## output: pdf_document
## always_allow_html: true
output: 
  rmdformats::html_clean:
    highlight: kate
---

```{r knitr_init, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

# Syllabus (FIN 332) Fundamentals of Investments
<br>
<br>
<center>
<b>SUNY POLYTECHNIC INSTITUTE</b>

<b>SCHOOL OF BUSINESS ADMINISTRATION</b>
</center>
<br>
<br>
**Instructor**: Matt Brigida, Ph.D.

**Office**: Donovan 1277

**Online Office Hours**: On request.
<!-- Tuesday 4--6pm -->

**Email**: matthew.brigida@sunypoly.edu

**Class Location**: Online.
<!-- *Hybrid*, DON 1157 -->

**Class Day/Time**: Asynchronous
<!-- Tuesday, 6:00---9:30pm -->

**Optional Text**: [*Investments* by Bodie, Kane, and Marcus, 8th edition (or later), ISBN: 0077261453](http://www.amazon.com/Investments-8th-Edition-Zvi-Bodie/dp/0077261453/ref=sr_1_5?ie=UTF8&qid=1407685749&sr=8-5&keywords=investment+bodie+kane+marcus)

The *Investments* text is optional, and all the material is available with appropriate prompts to an LLM.  That said, I recommend you pick up some edition of the text.  You can often find a used copy online for less than $10, and in this case it is well worth the money.

**Supplementary/Optional Materials**: 

-  [YouTube Lectures](https://www.youtube.com/playlist?list=PLRK1VeglPb4NO-D0HOn0QE9lQlBNR1vHK)
-  [Financial Education](https://financial-education.github.io/investments.html)
-  [39 Arbitrages](https://www.amazon.com/39-Arbitrages-Matthew-Brigida-Ph-D-ebook/dp/B08MWYN5D4/ref=sr_1_1?dchild=1&keywords=39+arbitrages&qid=1614011029&sr=8-1&tag=duckduckgo-20)

<!-- ## Video Walkthrough of Syllabus -->

<!-- ```{r} -->
<!-- library(vembedr) -->
<!-- # use _suggest_embed() with the video's link -->
<!-- embed_youtube("4nHWC1Oeqt0") -->
<!-- ``` -->

## Description

An introductory survey of the fundamental principles of investment management.
The learning outcomes for this course are summarized below:

#.  Understanding the structure of various capital markets, as well as how and why organizations
(ranging from individuals to multinational firms) participate in these markets. Particular importance will
be assigned to innovations in market structures (dark pools, ECNs) and their implications for market
participants. The student will be able to set up buy and sell orders for various securities, as well as
understand the use of leverage inherent in margin accounts and some derivative securities.
#. To extend previous study on equity and fixed income security valuation. Further, we will introduce
and value hybrid securities which have characteristics of both debt and equity (particularly convertible
bonds). Valuing the warrant in a convertible bond will also serve as a prelude to derivative securities.  
#. Quantify the interest rate risk in fixed income securities using duration and convexity. Moreover, the
student will be able to discuss the allocation of interest rate risk between lender and borrower in fixed
rate as compared to adjustable rate securities.
#. Assess reinvestment risk in fixed income securities and the benefits inherent in the option to prepay. 
#. This course will also introduce exchange­listed derivative securities (futures and options), along with
basic hedging and speculation strategies using these securities. Students will also learn about the
markets wherein derivatives are traded, and how laws governing these markets may differ from the laws
governing the stock markets. A basic introduction to valuing futures on storable commodities,
currencies, and interest rates will be afforded. We will then briefly discuss futures on non­storable commodities (particularly electricity). Lastly, using Excel students will apply the Black­Scholes (1973)
option pricing model to valuing options on non­dividend paying stock. The assumptions of
Black­Scholes (1973) will be discusses along with a non­rigorous introduction to risk neutral pricing
(intended to motivate further study).
#. Students will be able to measure the risk and return of individual securities as well as of a portfolio of
multiple risky securities. The effect of forming a portfolio on risk and expected return will be quantified,
as well as the resulting implications for forming an efficient portfolio. We will derive the Capital Asset
Pricing Model (CAPM) and thereby calculate the expected return for individual securities. A short
discussion of the assumptions of the CAPM and the alternative 'Arbitrage Pricing Theory' (APT) will
conclude.

## Course Objectives and Learning Outcomes:

Upon successful completion of the course each student will be able to:

1. Understand and express factual knowledge, principles and theories in the area of investments,

2. Exhibit creative problem-solving skills and refined reasoning capabilities in the area of investment selection and management,

3. Recognize the need for a broad-based, general education as a useful tool to understand the financial markets,

4. Understand the growing importance of globalization on both the investment process and on security markets,
 
5. Show an awareness of the various issues and developments that constantly reshape financial markets and investment choices.

## Learning Goals and Objectives
<center>

```{r goals, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Goal or Objective | Assessed by |
|------|-------|
| Goal 1.0: Demonstrate Business Disciplinary Competence | The exams and homeworks will evaluate both equity and fixed income security valuation. |
| Goal 3.0 (Objectives 3.1 and 3.2): Communicate Effectively Orally and in Written Form |  The presentation of a student created Excel spreadsheet to  calculate stock option prices using the Black-Scholes(1973) model |
| Goal 4.0 Objectives 4.1 and 4.3): Demonstrate Analytical Thinking Skills | Students will learn to value securities by the principle of no­arbitrage. Further, students will discern which derivative securities may be valued by no­arbitrage and which may not|
| Goal 5.0: Understand Global Issues in the Functional Areas of Business |  New exchanges spanning of multiple continents (e.g. NYSE Euronext) will be discussed with particular attention being paid to their effect on the investment landscape. |
| Goal 6.0 (Objectives 6.1 and 6.3): Demonstrate Effective Use of Technology and Data Analysis |  In both homeworks and these project, students will value complex securities using Excel. |
| Objectives 1.1 (knowledge of a key business discipline), 4.1 (interpretation of evidence), 4.3 (formulation of conclusions), and 6.3 (understanding data analysis) |  Students will measure both individual asset and portfolio risk and return. Through analyzing the effect of portfolio construction on risk and return, students will derive the CAPM. After a discussion of the assumptions of the CAPM, students will weigh the model against the APT. |

"
cat(tabl)
```
</center>

<!-- ## Exams -->

<!-- There will be one final exam. Normally no make-up exams will be given.  Failure to take an exam will result in a grade of zero for the missed exam.  Make-up exams will only be allowed for *extraordinary* and *verifiable* reasons. -->

<!---
\begin{center}
{\bf HOMEWORK} 
\end{center}
\begin{itemize}
\item {\bf Written:} Three written homework assignments will be assigned during the semester (they will be
end-of-chapter problems from the text). The three homework assignments will be due the week before
each exam. Each homework will be worth 3 and 1/3 final grade points. Late homework will not be
accepted.
%
-->

## Project 1: Trading Assignments

Trading assignments are here: https://github.com/Matt-Brigida/fin-332-trading-assignments  Students will complete each of these during the semester.  **If you do not make the trades you will receive a 0 for the assignment even if you attempt to answer some of the questions**.  

*Market Trading Hours*: The stock and option markets are open from 9:30 am to 4pm each non-holiday weekday.  Therefore, you must make your trades within these times.

<!-- I may assign other several homeworks throughout the semester that involve either trading in your brokerage accounts, or downloading data in R and performing some calculation/analyses. If I give pop quizzes, these grades will be included here.  -->

Here is a video on the first 3 trading assignments: https://www.youtube.com/watch?v=uG7l0WaATDs

```{r eval=FALSE}
# suggest_embed("https://www.youtube.com/watch?v=uG7l0WaATDs")
embed_youtube("uG7l0WaATDs")
```

And a video on shorting stock: https://www.youtube.com/watch?v=bTP19kqiKEk

```{r eval=FALSE}
# suggest_embed("https://www.youtube.com/watch?v=bTP19kqiKEk")
embed_youtube("bTP19kqiKEk")
```


### Brokerage Accounts

We will use paper trading accounts provided by Interactive Brokers. These
trading accounts are the exact same as the actual brokerage accounts---except the money isn’t real.
You will have access to (and real data from) stock, bond, commodity, and foreign exchange markets.
While the data alone is worth a fair amount of money, Interactive Brokers is offering the accounts to us
for free. Keep this in mind while following the directions to set up your account customer service will
be nonexistent. **If you lose your password, or forget your username, etc, you will not have an
account for the semester.** In this case you will have to trade in another student’s account, or mine.
Please pay attention while setting up your account, and write everything down.

See [**here**](#brti) example of the data we can pull using our IB accounts.  You may want to think if interesting projects/analyses you can do with access to such data.

[Also check out the IB Quant Blog.  It is a very good resource.](https://www.ibkr.com/quant)

## Project 2: Earnings Announcement Event Study

Each student will complete an event study on a U.S. common stock whose ticker begins with the same first letter as the student’s last name. The event is the company’s most recent earnings announcement prior to the start of the semester. If no suitable NYSE- or Nasdaq-listed common stock is available for that letter, the student should use the next letter in the last name. If that also fails, the student should contact the instructor for an approved fallback ticker. ETFs, mutual funds, ADRs, preferred shares, and OTC stocks may not be used.

The purpose of the project is to measure how the stock reacted to its most recent earnings news. Students must identify the earnings announcement date using the company’s investor relations page, earnings press release, or SEC filing. The event date is defined as the **first trading day on which the market could react to the earnings news**. If the earnings release was issued **before the market opened**, that trading day is day 0. If the earnings release was issued **after the market closed**, the next trading day is day 0.

Students will use **daily adjusted closing prices** for both the stock and the market benchmark, **SPY**, to compute returns. Daily stock return is:

$$
R_{i,t} = \frac{P_{i,t}}{P_{i,t-1}} - 1
$$

and daily market return is:

$$
R_{m,t} = \frac{P_{m,t}}{P_{m,t-1}} - 1
$$

where $P_{i,t}$ is the adjusted close for the stock on day $t$, and $P_{m,t}$ is the adjusted close for SPY on day $t$.

Students will calculate **abnormal return** for each day in the event window using the market-adjusted model:

$$
AR_t = R_{i,t} - R_{m,t}
$$

The required event window is **[-1, +1]**, where:

- **-1** = the trading day before the event
- **0** = the event day
- **+1** = the trading day after the event

Students must calculate:

1. the stock’s return on day -1, day 0, and day +1  
2. SPY’s return on day -1, day 0, and day +1  
3. abnormal return on day -1, day 0, and day +1  
4. the cumulative abnormal return over the three-day window:

$$
CAR[-1,+1] = AR_{-1} + AR_0 + AR_{+1}
$$

Each student must submit:

1. a spreadsheet showing all calculations  
2. the source for the earnings announcement date  
3. a chart showing either the three abnormal returns or the cumulative abnormal return over the event window  
4. short responses to the following questions:
   - Was the market reaction to the earnings announcement positive or negative?
   - Was most of the reaction concentrated on day 0, or did it spill over to day -1 or day +1?
   - Does the result appear consistent with semi-strong-form market efficiency?

A successful project will correctly identify the event date, correctly compute stock returns, market returns, abnormal returns, and $CAR[-1,+1]$, and provide a brief interpretation of the market’s reaction to the earnings announcement.


<!--
## Project 3: Black-Scholes Project

First, choose a stock whose ticker starts with the same letter that your last name starts with.  For example, since my last name is Brigida I may choose Boeing (ticker BA).  Once you have chosen your stock create a spreadsheet which will:

1.  Value an option on the stock using the Black-Scholes (1973) option pricing model.
2.  Calculate the stock's historical annualized volatility, and get an estimate of the implied volatility. To do so the you must show it is able to download a recent time series of the underlying stock price, convert these prices into a time series of returns, calculate the standard deviation of the returns, and then annualize the standard deviation (this is the stock annualized volatility which is a parameter in the option pricing model).
3.  [Calculate the value of the option by Monte Carlo.](https://www.youtube.com/watch?v=vLCXAKzaW5A).  [Background on the valuation.](https://www.youtube.com/watch?v=HOSf-lk9JOw)
4.  Calculate the proportion of your stock's return variance which is from the market and which is due to firm specific uncertainty.

You should be ready to explain any part of the spreadsheet.  For 4. consider the following regression:

$r_s = \alpha + \beta_s r_m + e_s$

where $r_s$ are returns on your stock and $r_m$ are market returns.  Then:

$Var(r_s) = (\beta_s)^2 Var(r_m) + Var(e_s)$

because:

$Cov(r_m, e_s) = 0$

Note, $Var(X)$ denotes the variance of $X$, and is also often written as $\sigma^2_X$.

$(\beta_s)^2 Var(r_m)$ is the market's contribution to your stock's variance, and:

$Var(e_s)$  is the firm specific contribution.
-->

## Project 3: Currency Markets and Multinational Hedging

Multinational corporations routinely face two intertwined risks: exchange rate movements and interest rate differentials across countries. This project asks you to explore both risks using real market data and the theoretical framework of Interest Rate Parity (IRP).

### Part 1: Interest Rate Parity

Interest Rate Parity is a no-arbitrage condition linking spot exchange rates, forward exchange rates, and interest rates in two countries. The **Covered Interest Rate Parity (CIP)** condition states:

$$
F = S \times \frac{1 + r_d}{1 + r_f}
$$

where $S$ is the current spot exchange rate (domestic currency per unit of foreign currency), $F$ is the forward exchange rate for the same maturity, $r_d$ is the domestic interest rate, and $r_f$ is the foreign interest rate.

Select a currency pair of your choice (e.g., USD/EUR, USD/GBP, USD/JPY). Using current market data:

1. Look up the current **spot exchange rate** for your currency pair.
2. Look up a **short-term interest rate** (e.g., 3-month government bill yield or interbank rate) for each of the two countries.
3. Compute the **CIP-implied forward rate** using the formula above.
4. Look up the actual **3-month forward rate** quoted in the market (forward rates are widely published for major currency pairs).
5. Compare your CIP-implied forward rate to the market forward rate. Are they close? If there is a discrepancy, discuss whether a covered interest arbitrage profit would theoretically be available, and why such deviations are rare in practice for major currency pairs.

### Part 2: Hedging a Foreign Currency Cash Flow

Suppose a U.S.-based multinational expects to receive a payment in the foreign currency you selected --- specifically, an amount equal to **1,000,000 units** of the foreign currency --- in exactly 90 days. The firm is concerned that the foreign currency will depreciate against the USD before payment is received, reducing the dollar value of the receipt.

Demonstrate how the firm can **lock in a dollar value today** using a forward contract:

1. Calculate the **unhedged dollar receipt** if the spot rate in 90 days equals today's spot rate (i.e., no change).
2. Calculate the **hedged dollar receipt** by applying the 3-month forward rate you looked up in Part 1.
3. Construct a simple scenario table showing the hedged vs. unhedged dollar receipt if the spot rate in 90 days is (a) 5% higher than today, (b) unchanged, and (c) 5% lower than today. In each scenario, compute the **gain or loss from hedging** relative to leaving the position unhedged.

### Part 3: Interest Rate Risk for a Multinational Borrower

Now consider the same multinational firm, which needs to borrow funds in the foreign currency. Suppose it borrows **1,000,000 units** of the foreign currency at a **floating interest rate** tied to a benchmark (such as EURIBOR or SONIA, depending on your currency pair). The firm is worried that foreign interest rates will rise before the next rate reset.

1. Briefly explain in your own words why a rise in the foreign benchmark rate increases the firm's borrowing cost and how this interacts with the exchange rate risk already present in Part 2.
<!---2. Describe (without necessarily pricing it) how an **interest rate swap** or a **cross-currency swap** could help the firm convert its floating-rate foreign-currency liability into a fixed-rate USD liability, thereby hedging both interest rate risk and currency risk simultaneously.-->
2. Using the interest rates from Part 1, calculate the firm's **all-in annual interest cost** (in USD terms) under the hedged position: assume the firm borrows at the foreign rate $r_f$, converts the proceeds at the spot rate, and has locked in repayment of the principal at the forward rate. Compare this to simply borrowing at the domestic rate $r_d$. Is the result consistent with CIP? Explain why or why not.

### Submission Requirements

Each student must submit:

1. A spreadsheet showing all data, calculations, and the scenario table from Part 2.
2. The sources for all market data (spot rate, forward rate, and interest rates), including the date on which the data were retrieved.
3. Short written responses (a few sentences each) to the discussion questions in Parts 1 and 3.

A successful project will correctly apply the CIP formula, correctly compute hedged and unhedged cash flows across scenarios, and provide a clear explanation of how forward contracts and swaps mitigate currency and interest rate risk for a multinational firm.


## Project 4: Portfolio Construction and CAPM Analysis

Each student will construct and evaluate a portfolio of common stocks. The purpose of the project is to measure how diversification affects risk and return, and to relate the portfolio’s expected return to its systematic risk.

Each student will choose **four U.S. common stocks**. At least **three different sectors** must be represented in the portfolio. ETFs, mutual funds, ADRs, preferred shares, and OTC stocks may not be used.

Students will use **daily adjusted closing prices** over the sample period January 1st 2026 through April 30 2026. Students will also use **SPY** as the market benchmark and the **3-month Treasury bill rate** as the risk-free rate.

Students must first calculate daily returns for each stock and for SPY:

$$
R_{i,t} = \frac{P_{i,t}}{P_{i,t-1}} - 1
$$

where $P_{i,t}$ is the adjusted closing price of asset $i$ on day $t$.

Students will then form an **equally weighted portfolio**, so that each of the four stocks has a portfolio weight of:

$$
w_i = 0.25
$$

The daily return on the portfolio is:

$$
R_{p,t} = \sum_{i=1}^{4} w_i R_{i,t}
$$

Students must calculate the following for the portfolio:

1. average daily return  
2. annualized average return  
3. daily standard deviation  
4. annualized standard deviation  

Annualized return should be calculated as:

$$
\bar{R}_{p,ann} = 252 \times \bar{R}_{p,daily}
$$

Annualized standard deviation should be calculated as:

$$
\sigma_{p,ann} = \sqrt{252}\,\sigma_{p,daily}
$$

Students must then estimate the portfolio’s beta by running the following regression:

$$
R_{p,t} - R_{f,t} = \alpha_p + \beta_p (R_{m,t} - R_{f,t}) + e_t
$$

where $R_{p,t}$ is the portfolio return, $R_{m,t}$ is the return on SPY, and $R_{f,t}$ is the daily risk-free rate implied by the 3-month Treasury bill rate.

Using the estimated beta, students must calculate the portfolio’s CAPM expected return:

$$
E(R_p) = R_f + \beta_p \left(E(R_m) - R_f\right)
$$

Students must compare the portfolio’s realized annualized return to its CAPM expected return and briefly discuss whether the portfolio outperformed or underperformed what CAPM would predict.

Students must also calculate the Sharpe ratio of the portfolio:

$$
Sharpe = \frac{\bar{R}_p - R_f}{\sigma_p}
$$

Each student must submit:

1. a spreadsheet showing all calculations  
2. a table with the four stocks and their sectors  
3. the portfolio’s annualized return, annualized standard deviation, beta, CAPM expected return, and Sharpe ratio  
4. one chart comparing the cumulative return of the portfolio to SPY over the sample period  
5. short responses to the following questions:
   - Did diversification reduce risk relative to the individual stocks?
   - Was the portfolio’s realized return above or below its CAPM expected return?
   - Would you consider this a strong portfolio for a passive investor? Why or why not?

A successful project will correctly calculate portfolio returns, annualized risk and return, beta, CAPM expected return, and the Sharpe ratio, and will provide a brief interpretation of the portfolio’s performance.

## Exam

There will be one multiple-choice exam covering important Investments topics.  The exam will be posted early in the course, and you will have until the due date to submit the exam.  If you do not submit the exam by the due date you will receive a 0.  Because you have over a month to take the exam, I won't allow late submissions for any reason.

<!-- ## Optional Web App Project -->

<!-- **Optional Projects are only for students doing well in the course.  They should not be used to attempt to increase your grade.** -->

<!-- Students will create a Shiny interactive web application.  To do so you'll first need to sign up for a free [shinyapps](https://www.shinyapps.io/) account. -->

<!-- You are free to create the account under a pseudonym, so no one can publicly identify you as the owner of the account.  However, the web application is a useful tool to show off your work, and is something that can go on your resume (with a link to the application).  So you may prefer to use your real name.  My user name is `mattbrigida`. -->

<!-- Your application should have something to do with financial markets, and should be at least somewhat original.  See this [gallery of applications](http://shiny.rstudio.com/). Possible applications may be: -->

<!-- - Plot a time series of stock prices, returns, or volatility. -->
<!-- - **Financial Advisers:**  Create an app which will return target asset allocation given a person's age and investing goals/risk tolerance. -->
<!-- - Create and plot a stock index. -->
<!-- - A Black-Scholes calculator. -->
<!-- - A margin calculator. -->
<!-- - Create a histogram or probability density plot for bond or stock returns. -->

<!-- To get started you will want to use the RStudio development environment for R.  This is available in the Still hall computer lab, or you can install it for free on your own computer [from here](https://www.rstudio.com/products/rstudio/download/).  If you install it on your own computer you'll need to install R first.  You can get [R here](https://cran.r-project.org/) -->

<!-- ## Optional Pairs Trade -->

<!-- Implement the pairs trade methodology outlined in Gatev et. al (2006). -->

<!-- @Article{Gatev_2006, -->
<!--   author       = {Gatev, Evan and Goetzmann, William N. and -->
<!--                   Rouwenhorst, K. Geert}, -->
<!--   title	       = {Pairs Trading: Performance of a Relative-Value -->
<!--                   Arbitrage Rule}, -->
<!--   year	       = 2006, -->
<!--   volume       = 19, -->
<!--   number       = 3, -->
<!--   pages	       = {797–827}, -->
<!--   issn	       = {1465-7368}, -->
<!--   doi	       = {10.1093/rfs/hhj020}, -->
<!--   url	       = {http://dx.doi.org/10.1093/rfs/hhj020}, -->
<!--   journal      = {Review of Financial Studies}, -->
<!--   publisher    = {Oxford University Press (OUP)} -->
<!-- } -->

<!-- ## Optional Optimal Portfolio -->

<!-- Construct a Markowitz Mean-Variance Optimal portfolio. -->

## Course Communication

All important/official announcements will either be posted on D2L or emailed to each student's SUNY Poly email account. All student questions (other than those that contain personal information) should be asked in class or posted to a discussion board.  Do not email me questions such as "When is the exam?".  These types of questions should be asked in class (or on a discussion board).  

### How to send an email

If you do send an email, be sure to include your course number (FIN 332) in the subject line.  Also you should send your email from your SUNY email account.  Emails from `gmail` or other similar addresses may not be read.  Lastly, make sure you are clear---for example if you are asking why you got a 0 on an assignment, be sure to include which assignment you are referring to. 

## Missed Classes

If you are not in class you are responsible for figuring out what you missed.  I will not email you a summary of what we covered in the class.  

## Re-Grading Assignments

I normally do not regrade assignments, however if I do so your grade may increase **or decrease** when regraded.  

## Grading

<center>

```{r grading, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Item | Points |
| ---- | ------ |
| Project 1 |  20 |
| Project 2 |  20 |
| Project 3 |  20 |
| Project 4 |  20 |
| Final Exam |  20 |
| Total Points | 100 |
"
cat(tabl)
```
</center>

<center>
**Final grades will be assigned according to the following scale**:
</center>

- 90 - 100 A
- 80 - 89.9 B
- 70 - 79.9 C
- 60 - 69.9 D
- < 60 F

> +/- grades may be assigned at the instructors discretion.


## An Important Note on Grading

There is no special consideration if you need a certain grade in this course to graduate.  **If you require a certain grade in this class to graduate it is your responsibility to earn that grade.** Specifically if you receive a `D` in this course I will not allow you to do extra assignments after the course is complete in exchange for a higher grade. 

## An Important Note on Late Work

In this course you have plenty of time to take exams and submit assignments.  Therefore, late work is not accepted and will receive a 0 grade.  Say, for example, you email me on the due date of an assignment or exam and say "I can't complete the assignment because the power went off at my house/dorm". You will receive a 0.  The takeaway from this is don't wait until the last day to submit work.

Again, I'll note the stock market closes at 4pm.  So let's say you wait until 5 pm on the due date of the trading assignments to start working---you will receive a 0 grade because you can't complete the trades.  

## A Note on Submitting Assignments

Before you submit an assignment I suggest you take a step back, open the document, and ask yourself can anyone easily understand the answers and how they were generated.  This is an important skill a financial analyst must have---the ability to organize a document to efficiently convey information.  That is also why I do not provide template for assignment submissions.  Constructing a readable document is part of the assignment.

## An Important Note on Meetings in 35W Courses

If you signed up for a 35W course this is *asynchronous*.  [This is the definition of a 35W course from the SUNY Poly website](https://sunypoly.edu/academics/online-learning/Online-and-Hybrid-Course-Descriptions.html):

> Online course are fully online and are asynchronous and have no meeting time (remotely or in-person). The activities must be completed by the due dates specified by your instructor. Online courses may also have proctored exams. Students will be required to locate their own proctors for the exams. 

> Depending on the instructor/department, the course may also use webinars to provide office hours, study sessions, presentations, group projects and recorded sessions. Contact the instructor or department for more information. The section number of online synchronous courses end with a "W"

Notice there are no meeting times.  If you want to meet by video I will try and set office hours to meet with students, but there is absolutely no guarantee we will be able to meet.  If you request a new video on a topic I can usually create one in a timely manner.

If you *need* to meet with me to take this course however, you should drop the 35W offering and sign up for a in-person or 35S or H offering of FIN 332.  One is guaranteed to be offered every other year.   


## Due Dates

- Project 1: 
- Project 2: 
- Project 3: 
- Project 4: 
- Final Exam:

<!-- ## Tentative Outline -->

<!-- **All due dates are in the ouline below.  There are no due dates listed in D2L.** -->

<!-- - 8/27: Chapter 1 -->
<!-- - 9/3:  Chapter 2 \& 3 -->
<!-- - 9/10: Chapter 3 \& 4 -->
<!-- - 9/17: Chapter 14 -->
<!-- - 9/24: (exam review)  -->
<!-- - 10/1: **10/03 (Exam 1)** & Chapter 15 -->
<!-- - 10/8 Chapter 16 -->
<!-- - 10/15: Chapter 20 -->
<!-- - 10/22: Chapter 21 -->
<!-- - 10/29: (exam review)  -->
<!-- - 11/5: **11/7 (Exam 2)** & Chapter 21 -->
<!-- - 11/12: Chapter 22 -->
<!-- - 11/19: Chapter 23 -->
<!-- - 11/26--12/8: Trading, exam review, **and the last day to present your projects.** -->
<!-- - 12/10: Finals Week -->

<!-- - 1/20: Chapter 1 -->
<!-- - 1/27:  Chapter 2 \& 3 -->
<!-- - 2/3:  Chapter 3 \& 4 -->
<!-- - 2/10: Chapter 14 -->
<!-- - 2/17: **Exam 1** -->
<!-- - 2/24: Chapter 15 -->
<!-- - 3/2:  Chapter 16 -->
<!-- - 3/19: Spring Break? -->
<!-- - 3/16: Chapter 20 -->
<!-- - 3/30: Chapter 21 -->
<!-- - 4/6: **Exam 2**  -->
<!-- - 4/13:Chapter 22  -->
<!-- - 4/20: Chapter 23 -->
<!-- - 4/27: Trading, exam review, **and the last day to present your projects.** -->

<!-- - Week 1: Chapter 1 -->
<!-- - Week 2: Chapter 2 \& 3 -->
<!-- - Week 3:  Chapter 3 \& 4 -->
<!-- - Week 4:  Review and Market Microstructure (*The Only Game in Town* and Payment for Order Flow) -->
<!-- - Week 5:  <span style="color:red">**Exam 1 Due, September 27** | **Trading Assignments 1, 2 and 3 are also due September 27**</span> -->
<!-- - Week 6:  Chapter 20: Options and Option Markets, 20.1--20.3 -->
<!-- - Week 7:  Chapter 20: Options and Option Markets, 20.4--20.7 -->
<!-- - Week 8:  Chapter 21: Options and Option Markets, 21.1--21.3 -->
<!-- - Week 9:  Chapter 21: Options and Option Markets, 21.4--21.6 -->
<!-- - Week 10: <span style="color:red">**Exam 2 Due, November 8** | **Trading Assignments 4 and 5 are also due November 8**</span> -->
<!-- - Week 11: Chapter 22: Futures, 22.1--22.2 -->
<!-- - Week 12: Chapter 22: Futures, 22.3--22.4 -->
<!-- - Week 13: Chapter 22: Futures, 22.5 and possibly a topic from Chapter 23 -->
<!-- - Week 14:  Trading, exam review, <span style="color:red">**Black-Scholes project Due December 3.** | **Trading Assignments 6 and 7 are also due December 3**</span> -->
<!-- - <span style="color:red">**Final Exam Due: Date TBA**</span> -->

## BRTI Tick Data {#brti}

Below are millisecond data for the Bitcoin Real-Time Index on Jan 3, 2018.  The data are pulled via the IB API.  With data of this type, you can dicover interesting features of market data---for example, notice the "last trade" is often outside of the bid/offer.  This is particularly important to understand when trading illiquid contracts, such as some options.  You can left-click your mouse, and drag, to zoom in on subintervals.

```{r error=FALSE, warning=FALSE, eval = TRUE}
library(dygraphs)

book <- readRDS("./jan_fut_12_18_book.rds")

dygraph(book['2018-01-03 09:30:00/2018-01-03 16:00:00'])

```

## Course Syllabus Disclosure Statement Spring 2022

>Accommodations for Students with Disabilities:

>In compliance with the Americans with Disabilities Act of 1990 and Section 504 of the Rehabilitation Act, SUNY Polytechnic Institute is committed to ensuring comprehensive educational access and accommodations for all registered students seeking access to meet course requirements and fully participate in programs and activities.  Students with documented disabilities or medical conditions are encouraged to request these services by registering with the Office of Disability Services. Please request accommodations early in the semester, or as soon as you become registered with Disability Services, so that we have adequate time to arrange your approved academic accommodation/s.  Once Disability Services creates your accommodation plan, it is your responsibility to provide me a copy of the accommodation plan.

>If you experience any access concerns that may require the need for adaptive or alternate format/presentation of materials, reach out to me or Disability Services right away. 

>For information related to these services or to schedule an appointment, please contact the Office of Disability Services using the information provided below.  The Office of Disability Services can accommodate virtual meeting requests.  The website has helpful information, and the link can be found here: https://sunypoly.edu/student-life/diversity-equity-inclusion/disabilities-services/contact-us.html

<!-- ## Answers to Online Questions -->

<!-- [On momentum trading strategies such as the post-earnings announcement drift anomaly.](https://www.youtube.com/watch?v=1sOqYRdnP_g&lc=Ugx7asEE_5LfM1d8DiN4AaABAg.8w_Di74z1tC8w__IIMlWOa) -->

<!-- [The CAPM does not assume all investors have the same degree of risk aversion](https://quant.stackexchange.com/a/46297/17448) -->

## General Notes (most relate only to in class sections)

#. The instructor is not involved in any way with your adding and dropping the course.  It is the student's responsibility to abide by all proper procedures and dates.
#. Attending class, and reading the text is required.
#. All exams will be closed book.
#. If you are late for an exam, no extra time will be allotted to you.
#. There will be no make up exams or extra points assignments.
#. You will be responsible for any material covered in class that is not in your text.
#. You should bring your text to class.
#. You are expected to be on time for class. This is especially important for exam
dates.
#. Disruptive behavior in the classroom will not be tolerated.
